Staged Abstract Interpreter

### 2018-01-27 paper/paper.tex
misc

\cite{Boucher:1996:ACN:647473.727587}'s work is esentially a partial evaluated
CE abstract interpreter written in a big-step semantics for CPS. The analysis
it can perform is monovariant. We reproduce their abstractly complied analysis
by adding explicit staging annotation to CE abstract interpreter.
Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.

>>>>

\cite{Boucher:1996:ACN:647473.727587}'s work is esentially a partial evaluated
CE (\textit{Control-Environment}) abstract interpreter written in a big-step semantics for CPS.
After the partial evluation, the \textit{Control} part of abstract interpreter
has been eliminated. 
The analysis it can perform is monovariant, sepcifically, 0-CFA.
Since the target language is written a continuation-passing style, so there is
no explict continuation component when constructing the abstract interpreter
(like CEK machine).

We reproduce their abstractly complied analysis
by adding explicit staging annotation to CE abstract interpreter.
Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.
